---
title: "The Effects of Supply on Medical Labor Markets"
subtitle: "Evidence from Dental School Closures in Finland"
author: 
   - name: Mikko Herzig
     affiliation: University of Turku, Finnish Institute for Health and Welfare Finnish Ministry of Finance
   - name: Konsta Lavaste
     affiliation: Finnish Institute for Health and Welfare
   - name: Allan Seuri
     affiliation: Tampere University, Ministry of Finance
date: today
date-format: long
lang: "en-US"
format:
   gfm:
      keep_md: true
      code-fold: show
      toc: false
editor: visual
license: MIT
keywords: ["labor supply", "universities", "dental schools", "healthcare", "physician", "earnings"]
---

## Preliminaries

First, let's load the setup and functions into memory.

```{r}
#| label: preliminaries
#| echo: true
#| output: false

# Load knitr
  library(knitr)

# Load here package for relative file paths
  library(here)

# Run setup script
  source(here("scripts", "00_setup.R"))

# Load functions
  source(here("scripts", "00_functions.R"))

```

## Map

In this section we create map of Finland which includes:

1.  locations of dental schools
2.  commuting zones

```{r}
#| label: map
#| echo: false
#| message: false
#| warning: false
#| output: true
#| results: false

# Which year's commuting zones we want to use (2013 is the earliest available)
  commutingzones_year <- 2013

# Run the script
  source(here("scripts", "01_map.R"))

```

## Timeline

In this section, we draw a graph which depicts the timeline of the closures and re-openings.

```{r}
#| label: timeline
#| echo: false
#| message: false
#| warning: false
#| output: true
#| results: false

# Which year we set as the first and the last year of the timeline
  timeline_year_begin <- 1990
  timeline_year_end <- 2020

# Run the script
  source(here("scripts", "02_timeline.R"))

```

## Student intake

In this section, we draw a graph which shows how the dental student intake has evolved over the years by school.

```{r}
#| label: intake
#| echo: false
#| message: false
#| warning: false
#| output: true
#| results: false

# Which year we set as the first and the last year of the timeline
  intake_year_begin <- 1990
  intake_year_end <- 2020

# Run the script
  source(here("scripts", "03_student_intake.R"))

```
