---
title: "The Effects of Supply on Medical Labor Markets"
author: 
   - Mikko Herzig (University of Turku)
   - Konsta Lavaste (Finnish Institute for Health and Welfare)
   - Allan Seuri (University of Tampere)
format: gfm
editor: visual
bibliography: grateful-refs.bib
---

Version: `r format(Sys.Date(), "%Y-%m-%d")`

## Preliminaries

Let's begin by loading the setup and custom functions into memory.

```{r}
#| label: preliminaries
#| echo: true
#| output: false

# Load here package for relative file paths
  library(here)

# Run setup script
  source(here("scripts", "00_setup.R"))

# Load functions
  source(here("scripts", "00_functions.R"))

```

## Map

In this section we create map of Finland which includes:

1.  locations of dental schools
2.  commuting zones

```{r}
#| label: map
#| echo: true
#| message: false
#| warning: false
#| output: true
#| results: false

# Which year's commuting zones we want to use (2013 is the earliest available)
  commutingzones_year <- 2013

# Run the script
  source(here("scripts", "01_map.R"))

```

## Timeline

In this section, we draw a graph which depicts the timeline of the closures and re-openings.

```{r}
#| label: timeline
#| echo: true
#| message: false
#| warning: false
#| output: true
#| results: false

# Which year we set as the first and the last year of the timeline
  timeline_year_begin <- 1990
  timeline_year_end <- 2020

# Run the script
  source(here("scripts", "02_timeline.R"))

```

## Student intake

In this section, we draw a graph which shows how the dental student intake has evolved over the years by school.

```{r}
#| label: intake
#| echo: true
#| message: false
#| warning: false
#| output: true
#| results: false

# Which year we set as the first and the last year of the timeline
  intake_year_begin <- 1990
  intake_year_end <- 2020

# Run the script
  source(here("scripts", "03_student_intake.R"))

```

## Dentist unemployment and vacancies

In this section, we draw a graph which shows how the dentist unemployment and the number of dentist vacancies has evolved over time.

```{r}
#| label: unemployment
#| echo: true
#| message: false
#| warning: false
#| output: true
#| results: false

# Which year we set as the first and the last year of the graph
  unemployment_year_begin <- 1990
  unemployment_year_end <- 2020

# Run the script
  source(here("scripts", "04_unemployment.R"))

```

## Dental care use and expenditures

To be added.

------------------------------------------------------------------------

# Package bibliography

```{r}
#| results: asis

cite_packages(output = "table", out.dir = ".", cite.tidyverse = TRUE)
```
